---
title: Data Visualization Using a Bar Chart
author: Bill Fisher
date: '2017-09-25'
slug: data-visualization-using-a-bar-chart
categories:
  - bar chart
  - ggiraph
  - ggplot
  - Lahman
  - dplyr
tags:
  - data sceince
---

Let's graph homeruns from the year 1980.

First, we need to bring in our downloaded pacakges using the library feature.

```{r message=FALSE,warning=FALSE}
library(Lahman)
library(dplyr)
library(ggiraph)
library(ggplot2)
```

Next, we need to extract the data we want to display from Lahman. During this step, we will also arrange our data ahead of time so that when we finally put our bar chart together, the homeruns will display from most to least.

```{r message=FALSE,warning=FALSE}
df<-Teams%>%
  filter(yearID==1980)%>%
  select(name,HR)%>%
  arrange(HR)
```

We will then convert our column name from a character to a factor.  You can check the current class by running:

```{r message=FALSE,warning=FALSE}
class(df$name)
```

To convert to a factor we will run:
```{r message=FALSE,warning=FALSE}
df$name<-factor(df$name,levels=df$name)
```

Finally, we will plot our graphs using ggplot.
```{r message=FALSE,warning=FALSE}
ggplot()+
  geom_bar(data=df,aes(x=name, y=HR),stat="identity", color="blue", fill="white")+
  coord_flip()
```

This looks good, but it can be hard for a user to tell exactly how many homeruns a given team had.  To fix this, we can use the package "ggiraph" and make our chart interactive.

Some things to remember for our ggplot code:
- save our bar chart into a recognizeable variable so it will be easy to call going forward
-change our graph type to "interactive"
- add-in the tooltip that we want
- add-in the data_id name that we want to display

```{r message=FALSE,warning=FALSE}
g<-ggplot()+
  geom_bar_interactive(data=df,aes(x=name,y=HR,tooltip=HR,data_id=name), stat="identity", color="blue", fill="white")+
  coord_flip()+
  ggtitle("1980 Team Homeruns")+
  xlab("Homeruns")+
  ylab("Team")

ggiraph(code=print(g),hover_css="fill:blue;stroke:white")
```

