---
title: Data Visualization Using a Histogram
author: Bill Fisher
date: '2017-09-25'
slug: data-visualization-using-a-histogram
categories:
  - ggiraph
  - ggplot
  - Lahman
tags:
  - data sceince
---

Let us say we wanted to graph the weight of all baseball players to ever play.  A nice display of this information could be in a histogram.

First, we need to install the necessary packages and call them in using "library()".

```{r message=FALSE,warning=FALSE}
library(Lahman)
library(dplyr)
library(ggiraph)
library(ggplot2)
```

Next, we can use our select function to select the players's weights, in the "Master" table.  We can also make sure that we exclude any players that we do not have data available for.

```{r message=FALSE,warning=FALSE}
df<-Master%>%
  filter(!is.na(weight))%>%
  select(weight)
```

Now, we can graph this information using ggplot and ggiraph.  To make our histogram more appealing we will set the outside color of our bars to white and fill them with blue.  Make sure to use geom_histogram to make a histogram and use data = df since that is what we already named our table.  You can also pick a precise number of bars for the histogram using "bins".  For our example, we will use 25.

```{r message=FALSE,warning=FALSE}
ggplot()+
  geom_histogram(data=df,aes(x=weight),color="white",fill="blue",bins=25)+
  ggtitle("Baseball Player Weights")
```
